The Sloan Digital Sky Survey Spectroscopic Reduction Pipeline

### 2006-04-01 doc/paper/paper2d.tex
Update.

The PRIMTARGET bit values are as follows (in hex and decimal):
\begin{verbatim}
  QSO_HIZ           = 0x1          = bit # 0 =        1
  QSO_CAP           = 0x2          = bit # 1 =        2
  QSO_SKIRT         = 0x4          = bit # 2 =        4
  QSO_FIRST_CAP     = 0x8          = bit # 3 =        8
  QSO_FIRST_SKIRT   = 0x10         = bit # 4 =       16
  QSO_MAG_OUTLIER   = 0x2000000    = bit #25 = 33554432
  QSO_REJECT        = 0x20000000   = bit #29 =536870912
  GALAXY_RED        = 0x20         = bit # 5 =       32
  GALAXY_RED_II     = 0x4000000    = bit #26 = 67108864
  GALAXY            = 0x40         = bit # 6 =       64
  GALAXY_BIG        = 0x80         = bit # 7 =      128
  GALAXY_BRIGHT_CORE= 0x100        = bit # 8 =      256
  ROSAT_A           = 0x200        = bit # 9 =      512
  ROSAT_B           = 0x400        = bit #10 =     1024
  ROSAT_C           = 0x800        = bit #11 =     2048
  ROSAT_D           = 0x1000       = bit #12 =     4096
  ROSAT_E           = 0x8000000    = bit #27 =134217728
  STAR_BHB          = 0x2000       = bit #13 =     8192
  STAR_CARBON       = 0x4000       = bit #14 =    16384
  STAR_BROWN_DWARF  = 0x8000       = bit #15 =    32768
  STAR_SUB_DWARF    = 0x10000      = bit #16 =    65536
  STAR_CATY_VAR     = 0x20000      = bit #17 =   131072
  STAR_RED_DWARF    = 0x40000      = bit #18 =   262144
  STAR_WHITE_DWARF  = 0x80000      = bit #19 =   524288
  STAR_PN           = 0x10000000   = bit #28 =268435456
  SERENDIP_BLUE     = 0x100000     = bit #20 =  1048576
  SERENDIP_FIRST    = 0x200000     = bit #21 =  2097152
  SERENDIP_RED      = 0x400000     = bit #22 =  4194304
  SERENDIP_DISTANT  = 0x800000     = bit #23 =  8388608
  SERENDIP_MANUAL   = 0x100000     = bit #24 = 16777216
  QSO_MAG_OUTLIER   = 0x200000     = bit #25 = 33554432
  GALAXY_RED_II     = 0x400000     = bit #26 = 67108864
  ROSAT_E           = 0x800000     = bit #27 =134217728
  STAR_PN           = 0x1000000    = bit #28 =268435456
  QSO_REJECT        = 0x2000000    = bit #29 =536870912
  SOUTHERN_SURVEY   = 0x8000000    = bit #31 =-2147483648
\end{verbatim}

>>>>

The PRIMTARGET bit values are as follows (in hex and decimal):
\begin{verbatim}
  QSO_HIZ           = 0x1          = bit # 0 =        1
  QSO_CAP           = 0x2          = bit # 1 =        2
  QSO_SKIRT         = 0x4          = bit # 2 =        4
  QSO_FIRST_CAP     = 0x8          = bit # 3 =        8
  QSO_FIRST_SKIRT   = 0x10         = bit # 4 =       16
  GALAXY_RED        = 0x20         = bit # 5 =       32
  GALAXY            = 0x40         = bit # 6 =       64
  GALAXY_BIG        = 0x80         = bit # 7 =      128
  GALAXY_BRIGHT_CORE= 0x100        = bit # 8 =      256
  ROSAT_A           = 0x200        = bit # 9 =      512
  ROSAT_B           = 0x400        = bit #10 =     1024
  ROSAT_C           = 0x800        = bit #11 =     2048
  ROSAT_D           = 0x1000       = bit #12 =     4096
  STAR_BHB          = 0x2000       = bit #13 =     8192
  STAR_CARBON       = 0x4000       = bit #14 =    16384
  STAR_BROWN_DWARF  = 0x8000       = bit #15 =    32768
  STAR_SUB_DWARF    = 0x10000      = bit #16 =    65536
  STAR_CATY_VAR     = 0x20000      = bit #17 =   131072
  STAR_RED_DWARF    = 0x40000      = bit #18 =   262144
  STAR_WHITE_DWARF  = 0x80000      = bit #19 =   524288
  SERENDIP_BLUE     = 0x100000     = bit #20 =  1048576
  SERENDIP_FIRST    = 0x200000     = bit #21 =  2097152
  SERENDIP_RED      = 0x400000     = bit #22 =  4194304
  SERENDIP_DISTANT  = 0x800000     = bit #23 =  8388608
  SERENDIP_MANUAL   = 0x100000     = bit #24 = 16777216
  QSO_MAG_OUTLIER   = 0x200000     = bit #25 = 33554432
  GALAXY_RED_II     = 0x400000     = bit #26 = 67108864
  ROSAT_E           = 0x800000     = bit #27 =134217728
  STAR_PN           = 0x1000000    = bit #28 =268435456
  QSO_REJECT        = 0x2000000    = bit #29 =536870912
  SOUTHERN_SURVEY   = 0x8000000    = bit #31 =-2147483648
\end{verbatim}
